% Commented as requested by the teacher
% \subsubsection{Segmentation of 2D images}

% Commented to make it more concise
% The segmentation and classification of intracranial hemorrhage (ICH) using CT imaging has been the subject of extensive research, leading to various methodologies aimed at improving diagnostic accuracy.

A significant number of studies have focused on the segmentation of hemorrhagic lesions. This serves as a foundational step toward volume estimation and outcome prediction. For instance, Yu et al. \cite{Yu2022} demonstrates effective segmentation techniques using a UNet for identifying ICH in brain CT scans. Similarly, Yao et al. \cite{YAO2020101910} present an automated approach that enhances the segmentation process, highlighting the importance of accurate delineation in improving clinical outcomes.

% Commented as requested by the teacher
% \subsubsection{Segmentation with 3D images}

In terms of advanced imaging techniques leveraging multiple images (3D images or sequences), Lu et al. \cite{9210782} provide a compelling argument for the application of data augmentation strategies by mirroring the original CT image, which can enhance model performance. Furthermore, models like the improved 3D U-Net and those utilizing squeeze-and-excitation blocks have demonstrated promising results in achieving precise segmentation and volume measurements \cite{ABRAMOVA2021101908}.

% Commented as requested by the teacher
% \subsubsection{Classification of 2D images}

Conversely, the classification of intracerebral and intracranial hemorrhages have been explored through various approaches. For example, Thabarsa et al. \cite{Thabarsa2023299} illustrate how support vector machines (SVM) have been effectively utilized to classify intracerebral hemorrhages based on radiomic features. Additionally, Seymur et al. \cite{Seymour2022} showcase the application of multiple machine learning techniques, including random forests, K-nearest neighbors (KNN), support vector machines, multilayer preceptrons, naive bayes and logistic regression for predicting outcomes related to intracranial hematoma expansion.

% Recent advances in deep learning have also enabled more robust approaches for ICH classification. The study of Zhong et al. \cite{Zhong2021} exemplifies the successful use of convolutional neural networks (CNNs) for this purpose. Moreover, Ma et al. \cite{Ma2022} further emphasize the capability of CNNs to predict hematoma expansion accurately.

% Commented as requested by the teacher
% \subsubsection{Classification of 3D images}

Despite the progress made in classification using single images, there is a scarcity of studies focusing on the classification of ICH with multiple CT slices. The work done by Grewal et al. \cite{8363574}, highlights the potential of utilizing multiple images in achieving higher accuracy, primarily through recurrent neural networks such as Long Short-Term Memory (LSTM) models. In a similar vein, Zhou et al. \cite{Zhou2024}, demonstrate the application of both 3D CNNs and Swin Transformers, as well as remarking the benefits of multi-view approaches in medical image analysis.

